\Huge \textbf{Hybrid rendering}\\ \huge using Radeon Rays

### 2018-11-03 Paper/Paper_BillietStijn_RadeonRays.tex
Worked on paper (Case study)

\subsection{Coordinate systems}

@@

@@

\subsection{Optimizations}

>>>>

@@

\subsection{Coordinate systems}
Although you can render without a proper coordinate system in place, the implementation needed world space coordinates rather than screen space. \newline\par
So for this implementation a transform component was set in place. This transform component stands in relationship with the GameObject. This relationship allows us to add childs to the GameObject while maintaining the correct local transforms in the component. If the position of a said object was changed we go ahead and rebuild our worldmatrix while keeping in check if the object had a parent.\newline\par
The next part is the camera component, the camera component is in charge of holding the viewprojectionmatrix. Meaning that it is also in charge of holding the camera position and its settings.\newline\par
The final part to the puzzle is the mesh draw component. To create a meshdrawcomponent the programmer has to provide it with a mesh filter which is loaded by the model loading utilities mentioned prior. Then the final assembly is to build the worldviewprojectionmatrix (by multiplying the world, view and projection matrices with each other) and send it to the shader.

@@
